PANCHANGE_analysis

### 2020-11-03 PANCHANGE_analysis.Rmd
Added sensitivty model 1b Absolute scores PCL for 3, 6, 9 months

>>>>

# PCL prepan: sensitivity
## Regression: Absolute scores
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
#### Subset of participants 3 months prior to pandemic
```{r pcl model1b sum_score prepan - sensitivity 3 months}
# Regression coefficients
pcl_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_3months")
kable(pcl_prepan_model1b_explan_estimates)
pcl_prepan_model1b_explan_estimates

# Regression diagnostic statistics
pcl_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_3months")
kable(pcl_prepan_model1b_explan_reg_stats)
pcl_prepan_model1b_explan_reg_stats
```

#### Subset of participants 6 months prior to pandemic
```{r pcl model1b sum_score prepan - sensitivity 6 months}
# Regression coefficients
pcl_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_6months")
kable(pcl_prepan_model1b_explan_estimates)
pcl_prepan_model1b_explan_estimates

# Regression diagnostic statistics
pcl_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_6months")
kable(pcl_prepan_model1b_explan_reg_stats)
pcl_prepan_model1b_explan_reg_stats
```

#### Subset of participants 9 months prior to pandemic
```{r pcl model1b sum_score prepan - sensitivity 9 months}
# Regression coefficients
pcl_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_9months")
kable(pcl_prepan_model1b_explan_estimates)
pcl_prepan_model1b_explan_estimates

# Regression diagnostic statistics
pcl_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_9months")
kable(pcl_prepan_model1b_explan_reg_stats)
pcl_prepan_model1b_explan_reg_stats
```
